Brownian Dynein Model

### 2016-01-29 latex/paper.tex
a bit of inkscape to make the illustration for bothbound case.
a bit more diagramming
fix one word in text
edits from our meeting

\documentclass[11pt]{article}

@@

Hello world

\includegraphics[width=3cm]{../figures/code-bothbound}

>>>>

\documentclass[11pt,twocolumn]{article}

@@

\section{Both bound}

\begin{figure}
  \includegraphics[width=\columnwidth]{../figures/code-bothbound}
  \caption{Angles used in both-bound case.}\label{fig:bothbound}
\end{figure}

In the both-bound case, we use two angles, as illustrated in
Fig.~\ref{fig:bothbound}.

These are the distances to the tail domain from the near and far
binding domains:
\begin{align}
  L_n &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{nm}}} \\
  L_f &= \sqrt{L_s^2 + L_t^2 - 2L_sL_t\cos{\theta_{fm}}}
\end{align}
We use two angles to determine the position of the motor domain:
\begin{align}
  \cos\theta_n &= \frac{L^2 + L_n^2 - L_f^2}{2L L_n} \\
  \sin\theta_{n} &= \sqrt{1 - \cos^2\theta_{n}} \\
  \cos\theta_{ns} &= \frac{L_s^2 + L_n^2 - L_t^2}{2L_s L_n} \\
  \sin\theta_{ns} &=
  \begin{cases}
    +\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} < \pi \\
    -\sqrt{1 - \cos^2\theta_{ns}} & \theta_{nm} > \pi
  \end{cases}
\end{align}
Given these definitions, the position of the motor domain is given
simply by $\cos$ and $\sin$ of $\theta_n$ and $\theta_{ns}$:
\begin{align}
  X_{nm} &= L_s\left(
  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
  \right)
  \\
  Y_{nm} &= L_s\left(
  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
  \right)
\end{align}
Looking at their derivatives gives
\begin{align}
  \dot{X}_{nm} &= ??? L_s\left(
  \cos\theta_n\cos\theta_{ns} - \sin\theta_n\sin\theta_{ns}
  \right) \dot{\cos\theta_n}
  \\
  \dot{Y}_{nm} &= ??? L_s\left(
  \cos\theta_n\sin\theta_{ns} + \sin\theta_n\cos\theta_{ns}
  \right)
\end{align}

\section{One bound}

\begin{figure}
  \includegraphics[width=\columnwidth]{../figures/code-onebound}
  \caption{Angles used in one-bound case.}\label{fig:onebound}
\end{figure}

In the one-bound case, we use four angles, as illustrated in
Fig.~\ref{fig:onebound}.
